\documentclass[11pt,a4paper]{article}
\begin{document}
\begin{titlepage}
\title{Web Application: Levels of granularity}
\author{29236259}
\maketitle
\end{titlepage}


\section{Presentation Level}
\subsection{APPLICATION RICH WEB INTERFACE}
\begin{itemize}
\item When the user directs to the system through one of the widely used browsers, a login screen is displayed. 
\item The login screen will be developed with HTML 5 and CSS3
\item It will consist of textboxes for the username and password and a button to send the information to the server.
\end{itemize}
\section{Authentication Level}
\subsection{LDAP AUTHANTICATION}
\begin{itemize}
\item The system accesses the CS LDAP to validate and grant privilege to the logged in user.
\item When the user has been authenticated, pages are sent over to client browser over HTTPS
\end{itemize}
\section{Home Page Level}
\subsection{POSSIBLE ACTIONS ACCORDING TO PRIVILEGE}
\begin{itemize}
\item A student will be directed to a page where he/she will only be able to view leaf and aggregate marks.
\item Markers will be presented with options to either:
\begin{itemize}
\item Create an assessment 
\item Edit marks for a specific student through a search interface
\item Delete marks and a text-area for the reason for doing so.
\item Changes committed will be displayed immediately through the use of JavaScript and JSON. 
\end{itemize}
\item Lectures will be able to:
\begin{itemize}
\item Manage information about the course through an easy to use interface that will make use of JSON to send data back and forth. 
\item Manage assessments:
\begin{itemize}
\item The lecturer will determine how marks are aggregated.
\item Lecture will decide which assessments are the leaf assessments.
\item He will specify how much each leaf assessment contributes to the aggregated mark.
\end{itemize}
\item Generate report
\begin{itemize}
\item The report can be generated into either a PDF or CSV at any level of granularity.
\end{itemize}
\end{itemize}
\end{itemize}
\section{Application layer Level}
\subsection{PROTOCOLS TO BE USED}
\begin{itemize}
\item SOAP interface will be used through XML unmarshalling when accessed by other systems.
\item The application will run over, thus SOAP will run over HTTPS for a secure connection.
\end{itemize}
\end{document}
